Helmet Foam Case Study Report

### 2024-05-07 CS2 Final Draft.qmd
Update CS2 Final Draft.qmd
Merged changes

In this summary, log(cycle) has a positive relationship with stiffnessFrac, but that is only when frequency and amplitude are zero. The interactions of freq and amp with log(cycle) have negative coefficients, showing us that stiffness decreases more when compressions are faster and larger. Chemical index levels 2 and 3 (aka 100 and 121) interacted with log(cycle) also have negative coefficients, indicating that these foams lose stiffness faster than foam with index 79.

@@

The summary of this model shows a high significance in almost all of our coefficients through small p-values (less than 0.05). These small p-values suggest that these variables are significant predictors of our response variable. The only value that does not show a significant p-value is chemIndex, which we chose to keep because the interaction between chemIndex and log(cycle) is significant. This model has multiple interactions: porosity and log(cycle), frequency and log(cycle), and chemical index and log(cycle). These interactions show that if all other variables are held constant, there is a combined effect of these interactions on the response variable.

```{r, echo = FALSE}
Anova(dampingModel)
```

@@

**Question 2:** For stiffness, we see that the individual predictors on their own will increase the initial stiffness, but as time goes on, foam using chemical index 121 will have the greatest decrease in stiffness. The individual predictors will impact damping in a similar way but foam with a chemical index of 79 and a low porosity will see the greatest decay in damping. Overall, there appear to be significant impacts on the stiffness and damping values depending on chemical index and porosity.

>>>>

In this summary, log(cycle) has a positive relationship with stiffnessFrac, but that is only when frequency and amplitude are zero. The interactions of freq and amp with log(cycle) have negative coefficients, showing us that stiffness decreases more when compressions are faster and larger. Chemical index levels 2 and 3 (aka 100 and 121) interacted with log(cycle) also have negative coefficients, indicating that these foams lose stiffness faster than foam with index 79. However, these two chemical indices have higher stiffness right after compressions start, and foams with high frequency and amplitude do as well.

@@

```{r, echo = FALSE}
suppressWarnings(dampingModel <- lmer(log(stiffnessFrac) ~ factor(chemIndex) + freq + log(cycle) +  factor(chemIndex):log(cycle) + freq:log(cycle) + (1 + log(cycle)|ID), data = foam_data_scaled))
summary(dampingModel)$coef
```

\begin{center}
\text{Table 7: Coefficients for Damaping Fraction Model}
\end{center}

The summary of this model shows a high significance in almost all of our coefficients through small p-values (less than 0.05). These small p-values suggest that these variables are significant predictors of our response variable. Like the stiffness model, there are some predictors that do not have a significant p-value but their interaction terms are very significant. We can double check our predictors in the below table as well and see that all our predictors are significant.

```{r}
Anova(dampingModel)
```

\begin{center}
\text{Table 8: Anova Analysis of Damping Fraction Model}
\end{center}

@@

**Question 2:** High frequency, high amplitude, and chemical indices 100 and 121 all increase the initial stiffness, but as time goes on, these also lose stiffness the fastest. Foam with chemical index 121 has the greatest decrease in stiffness. The individual predictors will impact damping in a similar way but foam with a chemical index of 79 and a low porosity will see the greatest decay in damping. Overall, there appear to be significant impacts on the stiffness and damping values depending on chemical index and porosity.
